%-------------------------
% Resume in Latex
% Author : Matthew Lim
% Commit : https://github.com/limmabean/CoverLetterTemplate/commit/7f9445b9d4c4ace3c02ced1e7c9c7cbe73009fdf
% License : MIT
%------------------------

%------------------------
% Author : Fan JIN
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]

%-------------------------
% Custom commands



\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/goldsail}{\Large Fan~Jin}}   & +1-702-934-6263 \\
                                                                & 3869 Miramar St, Apt Artesa-F-111-3 \\
  \href{mailto:fan.jin.1997@gmail.com/}{fan.jin.1997@gmail.com} & La Jolla, CA 92037

\end{tabular*}


%-----------LETTER-----------------
\section{}
\vspace{10pt}
\large{
Dear XXX Hiring Manager, \newline

I am stunned when I watched your demo video of XXX.
I am applying for the SDE internship position for summer 2020 that you posted on Handshake.
\newline

During my previous internship at ByteDance, I worked on a web application in React with a large backend system in Go,
and became familiar with full-stack development, testing and deployment on Cloud in a team.
The Content Management System I built was designed as a single web application,
in which product statistics, configurations and logs are displayed visually and edited easily.
Not only did I gain experience in React JS, Go, Cloud, Redis, Kafka, Git, etc., 
but I also learned how to communicate and cooperate well with team leader and other developers.
\newline

In previous years, I did many programming work in university labs,
mainly in C++ and Java but also including Python and MATLAB.
In summer 2018 when visiting UC Berkeley, in particular,
I developed an autonomous driving simulator using Unreal Engine in C++.
Integrating an industry-level C++ framework to meet my needs was challenging,
but I made it in the end after quick learning about game engine and advanced C++ techniques in only 6 weeks.
This coding experience convinced me that I am motivated and prepared to get into the career of software engineering.
\newline

Now I am again looking for a place to help people and solve problems using my programming skills.
I am very excited for the opportunity to learn and I look forward to hearing back from you! 
Feel free to contact me by email or phone.
\newline

Best regards, \par
Fan Jin
}
\vspace{240pt}
\section{}

%-------------------------------------------
\end{document}