%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Commit : https://github.com/sb2nov/resume/tree/edde4be86b0593a9ae1af7c23fd57e8c74f514f3
% License : MIT
%------------------------

%------------------------
% Author : Fan JIN
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Fan Jin} & Email : \href{mailto:fan.jin.1997@gmail.com}{fan.jin.1997@gmail.com}\\
  \href{https://github.com/goldsail}{https://github.com/goldsail} & Mobile : +1-858-247-6514 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA}
      {Master of Science in Computer Science}{Aug. 2019 -- }
    \resumeSubheading
      {Tsinghua University}{Beijing, China}
      {Bachelor of Engineering in Automation;  GPA: 3.73 (Top 15\%); Minor in Statistics}{Aug. 2015 -- July. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ByteDance; Finance and Stocks Team}{Beijing, China}
      {Full-stack SDE Intern in Back-end Team}{Jun 2019 -- Sep 2019}
      \resumeItemListStart
        \resumeItem{Content Management System}{
          \begin{itemize}
            \item Our team builds Dolphin Stocks, an app for stocks investors in China with DAU 800k+.
            \item With the Content Management System I built,
            product managers can view statistics,
            customer service team can adjust order refunds (1k per day),
            and developers can edit configurations visually spending 50\% less time.
            \item Full-stack in ReactJS and Go, using Gin, Thrift, Redis, Kafka, consul. Deployed to container on Cloud.
          \end{itemize}
        }
        \resumeItem{Stock Quotation Monitor}{
          \begin{itemize}
            \item Monitors stock price and quotation from multiple data sources and validates consistency.
            \item With it, our 10-people team no longer needs to spend 1+ hours a day fixing wrong incoming data mannually.
            \item Written in Python with PySpider and the Kafka message queue.
          \end{itemize}
        }
      \resumeItemListEnd

    \resumeSubheading
      {University of California, Berkeley; Mechanical Systems Control Lab}{Berkeley, CA}
      {Visiting Student Developer}{Jul 2018 -- Sep 2018}
      \resumeItemListStart
        \resumeItem{Autonomous Driving Simulator in UE4}{
          \begin{itemize}
            \item Built an autonomous driving simulator using Unreal Engine 4 in C++ (CLion + Visual Studio).
            \item Designed the system with PhD students and implemented Render and Core server modules independently.
            \item Fixed a bug in the sample code of UE4, my pull request later merged on GitHub.
          \end{itemize}
        }
      \resumeItemListEnd

    \resumeSubheading
      {Course Projects}{}
      {with intense coding}{}
      \resumeItemListStart
        \resumeItem{Distributed Network Systems Course Project (CSE 224, Fall 2019)}{
          \begin{itemize}
            \item A distributed, fault-tolerant cloud storage system implemented in C++ using XMLRPC.
          \end{itemize}
        }
        \resumeItem{Undergrad Thesis Project (Spring 2019)}{
          \begin{itemize}
            \item Built An intelligent transportation simulation software featuring semi-physical simulation.
            \item Refactored decade-old codes into a new distributed architecture with nearly 10k lines of C++.
          \end{itemize}
        }
        \resumeItem{Compilor Course Project (Fall 2017)}{
          \begin{itemize}
            \item A compiler for some LL(0) VM-based language using recursive descent, implemented in Java.
            \item One-pass tokenizer, one-pass state-machine-based syntax analyzer, one-pass VM bytecode generator.
          \end{itemize}
        }
        \resumeItem{Microscope Controller App with VR Glasses (Spring 2017)}{
          \begin{itemize}
            \item An Android app in which researchers could see and control the microscope with VR glasses.
            \item Ported code from original microscope controller (desktop C++ in Qt) to Android app.
            \item The users control the microscope by rotating the phone so that they could focus on the field of view.
          \end{itemize}
        }
        \resumeItem{GPU Server Maintainer (2016 -- 2019)}{
          Maintained a GPU linux server in Microsoft Student Club.
          Helping others train their nueral network, I communicated with students and club leaders as well as gaining experience in Linux.
        }
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages and Tools}{: C/C++, Go, JavaScript, Java, R, Python, C\#, MATLAB, Bash, Git, CI/CD}
      }
    \item{
      \textbf{Frameworks}{: ReactJS, Ant Design, Thrift (RPC), Gin (web server), MySQL, Redis, Kafka MQ, Qt}
    }
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Relevant Courses}
\resumeSubHeadingListStart
  \resumeSubItem{EECS}{
    C/C++, Data Stucture and Algorithms,
    Computer Architecture, Systems and Signals,
    Digital Circuits
  }
  \resumeSubItem{Statistics}{
    Introduction to Data Science, Statistical Inference,
    Financial Statistics, Bayesian Statistics
  }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
